---
title: "Week 4"
output: html_notebook
---

```{r setup}
library(e1071)
library(readxl)
week4 <- read_excel("week4.xlsx")

drawChart=function(val, myStr){
  #Hist=hist(val, breaks="Scott", main=myStr)
  myHist=hist(val, breaks="Sturges", main=myStr)
  par(new=TRUE)
  curve(
    dnorm(x, mean(val), sd(val)),
    xlim=c(min(myHist$breaks), max(myHist$breaks)),
    xlab="", ylab="",
    xaxt="n", yaxt="n",
    bty="n"
  )

  boxplot(val, horizontal=T)
  par(new=T)
  stripchart(val, method="stack")
}

mySDsummary=function(x) {
  df = data.frame(
    "Mean"=mean(x),
    "Median"=median(x),
    "Mode"=names(which.max(table(x))),
    "Standard deviation"=sd(x),
    "Standard error"=sd(x)/sqrt(length(x)),
    "Variance"=var(x),
    "Kurtosis"=kurtosis(x),
    "Skewness"=skewness(x),
    "Min"=min(x),
    "Max"=max(x),
    "Total"=sum(x),
    "Length"=length(x)
  )
  
  return(df)
}

getSDinterval = function(val){
    return(c(
    val$Mean-1.96*val$Standard.deviation/sqrt(val$Length),
    val$Mean+1.96*val$Standard.deviation/sqrt(val$Length)
  ))
}

getTinterval=function(x){
  ret = t.test(x)
  print(ret)
  
  return (c(ret$conf.int[1], ret$conf.int[2]))
}

seekPrice=function(x){
  fte=15
  material=500
  logistic=100
  others=300
  
  return(x * fte + material + logistic + others)
}

myHour = week4$`ASM hours (Min)`
```

# 1. Get Interval (Low and High value) at 95% confidence level for mean ASM hours 
## Standard deviation case
```{r}
drawChart(myHour, "ASM hours")
df = mySDsummary(myHour)
print(df)
```

Minmum-Maximum ASM min rage in 95% confident interval is
```{r}
print(getSDinterval(df))
```

## T test case
Minimum-Maximum ASM min range in 95% confident interval is
```{r}
print(getTinterval(myHour))
```

# 2. Estimate the unit price of this toy for sales planning 
## Assumption
```{r}
topFTE1 = 18
midFTE1 = 20
wstFTE1 = 22
```
Standard deviation case and T test case output almost same FTE.  
Set FTE/product as following.

* `r topFTE1`: high performance
* `r midFTE1`: average performance
* `r wstFTE1`: low perfomance

* total = `r seekPrice(0)`/unit
  + Material cost = 500
  + Logistic cost = 100
  + Other costs = 300

```{r}
mat = matrix(c(
  seekPrice(topFTE1),
  seekPrice(midFTE1),
  seekPrice(wstFTE1)
), ncol=3)

colnames(mat)=c(
  "high perf",
  "avr perf",
  "low perf"
)

mat = rbind(mat, c(
  mat[1,1] / (1 - 0.3),
  mat[1,2] / (1 - 0.3),
  mat[1,3] / (1 - 0.3)
))

x = 10000
y = 0.95
z = 1 - y


mat = rbind(mat, c(
  x * z * mat[1,1] / x * y,
  x * z * mat[1,2] / x * y,
  x * z * mat[1,3] / x * y  
))

rownames(mat) = c(
  "break even cost/unit",
  "including 30 allowance",
  "offset cost for 5%"
)
```
## Direction
total X units production.  
95% for sale, 5% are for rejected, returned exchange, etc.  
Ex: total 3600 units, 95% (3420 units) for sale, 5% (180 units) are not.  
Add following cost To offset for 5%.
offset = 5 % * breake even cost per unit / 95%

## Pricing
`r data.frame(mat)`
30% allowance = 30% profit ratio  
* estimation: 1780 


